Effects of Tunable Hydrophobicity on the Collective Hydrodynamics of Janus Particles under Flows

### 2023-03-16 doc/PRF2022/PRF_main.tex
yuans edits to intro

\begin{abstract}
  Active colloidal systems with non-equilibrium self-organization is a
  long-standing, challenging area in biology. To understand how
  hydrodynamic flow may be used to actively control self-assembly of
  Janus particles (JPs), we use a model recently developed for the
  many-body hydrodynamics of amphiphilic JPs suspended in a viscous
  background flow (JFM, 941, 2022). We investigate how various
  morphologies arise from tuning the hydrophobic distribution of the
  JP-solvent interface. We find JPs assembled into uni-lamella,
  multi-lamella and striated structures. To introduce dynamics, we
  include a linear shear flow and a steady Taylor-Green mixing flow, and
  measure the collective dynamics of JP particles in terms of their (a)
  free energy from the hydrophobic interactions between the JPs, (b)
  order parameter for the ordering of JPs in terms of alignment of their
  directors, and (c) strain parameter that captures the deformation in
  the assembly. We characterize the effective material properties of the
  JP structures and find that the uni-lamellar structures increases
  orientation order under shear flow, the multilamellar structure
  behaves as a shear thinning fluid, and the striated structure
  possesses a yield stress. These numerical results provide insights
  into dynamic control of non-equilibrium active biological systems with
  similar self-organization.
\end{abstract}

@@

\section{Introduction}
% Put \label in argument of \section for cross-referencing
%\section{\label{}}
Janus particles are colloids combining two dissimilar chemical or
physical functionalities at their opposite
sides~\cite{KirillovaMarschelkeSynytska2019}. Self-propelling Janus
particles, for example, with a permanent biphasic asymmetry, have
emerged as a rich chemical platform for the exploration of active
matter~\cite{Meredithetal2022}.
In the absence of mobility and any
imposed flow, Janus particles (JPs) self-assemble
into oligomers of various geometries
and sizes
depending on the interactions between JPs and the 
viscous solvent~\cite{Bradley2017, KangHonciuc2018,
HongCacciutoLuijtenGranick2008},
with tunable functions for biomedical engineering
applications~\cite{GheisariSahfieeAbbasiEtAl2021_DMR,
LiuYangHuangEtAl2016_Angew, LiWangYaoEtAl2019_Nanoscale,
Bradley2016,Zarzaretal2015, KirillovaMarschelkeSynytska2019}.

When driven by an external flow, dynamic rearrangement of JPs emerges
naturally from the interactions between particles and fluid in colloidal
matter~\cite{RevModPhys.93.025008}. Such colloidal hydrodynamics
belong to a wide class of nonequilibrium self-organization in physics,
often with complexity and features similar to that of biological systems
such as living cells, bacterial baths, and animal
flocks~\cite{CollardGrosjeanVandewalle2020, Vutukuri2020}. A
long-standing challenge in fluid mechanics and material science is to
solve the ``inverse" problem of creating a model colloidal system that
will self-assemble into a prescribed
structure~\cite{PhysRevLett.128.256102}. For example, the framework of
geometrical frustration, which has been used to explain disordered
systems, could instead be used to design new, ordered systems, through
specific choices for the shapes or interactions of the
particles~\cite{Manoharan2015_Science}.

The surface of a Janus particle may have a dissimilar spatial
distribution of hydrophobicity~\cite{doi:10.1021/la503455h}. The
many-body hydrodynamics of amphiphilic Janus particles assembled as
vesicles suspended in a viscous fluid in the inertialess regime (zero
Reynolds number) has been studied using boundary integral numerical
simulations~\cite{Fu20,Fu2022_JFM}. The dynamics of the JP suspension
results from the combination of long-range hydrodynamic interaction and
non-local interactions between JPs through the distribution of a
hydrophobic attraction potential (HAP).
%
In a quiescent flow, numerical simulations of a JP suspension showed
self-assembly into micelles and bilayers of JPs that provide an
alternative means for computing the mechanical moduli of a colloidal
membrane~\cite{NaTr00, Fu20, KrFiGuKaHa13}. Under background flows, the
hydrodynamics of a JP vesicle (a self-enclosed bilayer of JPs) exhibit
many familiar behaviors of a vesicle: elongation and alignment along the
extensional direction, tank-treading, and rupture of a vesicle under
shear flow~\cite{Fu2022_JFM, grandmaison_brancherie_salsac_2021,
D2SM00179A,keller_skalak_1982, Finken08, Shaqfeh11}.

Molecular dynamics (MD) and Monte Carlo provide another avenue for
simulating the interaction between JPs, solvents, and
substrates~\cite{Brandner2019, Baniketal2021,
HongCacciutoLuijtenGranick2008, C9NR05885K}. These methods often use
pair-potentials to describe the interaction between JPs, for example by
prescribing angle dependent forces and torques that bring the
hydrophobic sides of two amphiphilic JPs into opposition. The HAP
formulation of the present work also has attractive, long-range forces
and torques, but they are instead derived from a boundary value problem
for the molecular structure of water~\cite{Ma77, GoHaKo94, ErLjCl89,
Lietal05, Israelachvili80}. Unlike in MD or Monte Carlo simulations, the
HAP interactions are nonadditive~\cite{Fu20}, so that the interactions
between a pair of JPs is affected by the presence of other particles.

\hl{Qi Wang has a preprint "A hybrid phase field method for fluid-structure interactions in viscous fluids"}.

In this work, we take advantage of the flexibility of the HAP model to
examine the effects of varying the distribution of hydrophobicity on JP
surfaces. Such variation of the boundary condition on JP surfaces has
been realized experimentally by using chemicals to adjust the polarity
of the viscous solvent~\cite{Zarzaretal2015,
KirillovaMarschelkeSynytska2019, doi:10.1021/la503455h}. We show that a
simple tuning of the hydrophobic distribution leads to transitions from
unilamellar to multilamellar or striated superstructures of JPs.
Focusing on the fluid-structure interactions that correspond to such
transitions, we investigate the deformation of these novel structures in
background flows and map out their collective behavior away from
equilibrium. Looking forward, including other fields like electric
potential for JPs synthesized with charged
polymers~\cite{HongCacciutoLuijtenGranick2008, doi:10.1021/la503455h,
KangHonciuc2018}, is straightforward within the context of the boundary
integral representations~\cite{kohl-cor-che-vee22}, opening further
lines of investigation.

>>>>

\begin{abstract}
  Active colloidal systems with non-equilibrium self-organization is a
  long-standing, challenging area in material sciences and biology. To understand how
  hydrodynamic flow may be used to actively control self-assembly of
  Janus particles (JPs), we developed  a model for the
  many-body hydrodynamics of amphiphilic JPs suspended in a viscous
  fluid with imposed far-field background flows (Journal of Fluid Mech., 941, 2022). 
  In this work we alter the hydrophobic distribution on the JP-solvent
  interface to investigate the hydrodynamics that underlies the various
  morphologies and rheological properties of the JP assembly in the
  suspension.
  We find JPs assemble into uni-lamella,
  multi-lamella, and striated structures. To introduce dynamics, we
  include a planar linear shear flow and a steady Taylor-Green mixing flow, and
  measure the collective dynamics of JP particles in terms of their (a)
  free energy from the hydrophobic interactions between the JPs, (b)
  order parameter for the ordering of JPs in terms of alignment of their
  directors, and (c) strain parameter that captures the deformation in
  the assembly. We characterize the effective material properties of the
  JP structures and find that the uni-lamellar structures increases
  orientation order under shear flow, the multilamellar structure
  behaves as a shear thinning fluid, and the striated structure
  possesses a yield stress. These numerical results provide insights
  into dynamic control of non-equilibrium active biological systems with
  similar self-organization.
\end{abstract}

@@

\section{Introduction}
% Put \label in argument of \section for cross-referencing
%\section{\label{}}
Janus particles are colloids with dissimilar chemical or
physical functionalities between the two sides of their surfaces
~\cite{deGennes1992,KirillovaMarschelkeSynytska2019}. Self-propelling Janus
particles, for example, with a permanent biphasic asymmetry, have
emerged as a rich chemical platform for the exploration of active
matter~\cite{Meredithetal2022} and mobility induced phase separation.
In the absence of mobility and any
imposed flow, Janus particles (JPs) self-assemble
into oligomers of various geometries
and sizes
depending on the interactions between JPs and the 
viscous solvent~\cite{Bradley2017, KangHonciuc2018,
HongCacciutoLuijtenGranick2008},
with tunable functions for biomedical engineering
applications~\cite{GheisariSahfieeAbbasiEtAl2021_DMR,
LiuYangHuangEtAl2016_Angew, LiWangYaoEtAl2019_Nanoscale,
Bradley2016,Zarzaretal2015, KirillovaMarschelkeSynytska2019}.

When driven by an external flow, dynamic rearrangement of JPs emerges
naturally from the interactions between particles and fluid in colloidal
matter~\cite{RevModPhys.93.025008}. Such colloidal hydrodynamics
belong to a wide class of nonequilibrium self-organization in physics,
often with complexity and features similar to that of biological systems
such as living cells, bacterial baths, and animal
flocks~\cite{CollardGrosjeanVandewalle2020, Vutukuri2020}. A
long-standing challenge in fluid mechanics and material science is to
solve the ``inverse" problem of creating a model colloidal system that
will self-assemble into prescribed
structures~\cite{PhysRevLett.128.256102}. For example, the framework of
geometrical frustration, which has been used to explain disordered
systems, could instead be used to design new, ordered systems, through
specific choices for the shapes or interactions of the
particles~\cite{Manoharan2015_Science}.

In this work we focus on collective hydrodynamics of immobile
amphiphilic JPs in a
viscous fluid under an imposed far-field flow. The amphiphilic JP has a
hydrophobic surface on one side and a hydrophilic surface on the other
side \cite{doi:10.1021/la503455h}.
The many-body hydrodynamics of amphiphilic Janus particles assembled as
vesicles (self-enclosed bilayers of JPs) suspended in a viscous fluid in the inertialess regime (zero
Reynolds number) has been studied using boundary integral numerical
simulations~\cite{Fu20,Fu2022_JFM}. The dynamics of the JP suspension
results from the combination of long-range hydrodynamic interaction and
non-local interactions between JPs through the distribution of a
hydrophobic attraction potential (HAP).
%
In a quiescent flow, a JP suspension 
self-assemble into micelles and bilayers of JPs that provide an
alternative means for computing the mechanical moduli of a colloidal
membrane in numerical simulations~\cite{NaTr00, Fu20, KrFiGuKaHa13}. Under background flows, the
hydrodynamics of a JP vesicle (a self-enclosed bilayer of JPs) exhibit
many familiar behaviors of a vesicle: elongation and alignment along the
extensional direction, tank-treading, and rupture of a vesicle under
shear flow~\cite{Fu2022_JFM, grandmaison_brancherie_salsac_2021,
D2SM00179A,keller_skalak_1982, Finken08, Shaqfeh11}.

Molecular dynamics (MD) and Monte Carlo simulations provide another avenue for
simulating the interaction between JPs, solvents, and
substrates~\cite{Brandner2019, Baniketal2021,
HongCacciutoLuijtenGranick2008, C9NR05885K}. In these methods 
pair-potentials are used to describe the interaction between JPs, for example by
prescribing angle dependent forces and torques that bring the
hydrophobic sides of two amphiphilic JPs into opposition. On the other
hand, the HAP
formulation of the present work has attractive, long-range forces
and torques, and they are instead derived from a boundary value problem
for the molecular structure of water~\cite{Ma77, GoHaKo94, ErLjCl89,
Lietal05, Israelachvili80}. Unlike in MD or Monte Carlo simulations, the
HAP interactions are nonadditive~\cite{Fu20}, so that the interactions
between a pair of JPs is affected by the presence of other particles. 
As such, the HAP is a phase-field function that represents the
properties of the solvent in the presence of JPs. Such approach falls
into the category of work that considers particles as a discretization
of a continuum problem~\cite{HongWang2021_arXiv}.

%\hl{Qi Wang has a preprint "A hybrid phase field method for fluid-structure interactions in viscous fluids"}.

Here we take advantage of the flexibility of the HAP model to
examine the effects of tuning the distribution of hydrophobicity on JP
surfaces. Such variation of the boundary condition on JP surfaces has
been realized experimentally by using chemicals to adjust the polarity
of the viscous solvent~\cite{Zarzaretal2015,
KirillovaMarschelkeSynytska2019, doi:10.1021/la503455h}. We show that a
simple tuning of the hydrophobic distribution leads to transitions from
unilamellar to multilamellar or striated superstructures of JPs.
Focusing on the fluid-structure interactions that correspond to such
transitions, we investigate the deformation of these novel structures in
background flows and map out their collective behavior away from
equilibrium. Looking forward, including other fields like electric
potential for JPs synthesized with charged
polymers~\cite{HongCacciutoLuijtenGranick2008, doi:10.1021/la503455h,
KangHonciuc2018}, is straightforward within the context of the boundary
integral representations~\cite{kohl-cor-che-vee22}, opening further
lines of investigation.

This paper is organized as follows. \S~II summarizes the general
mathematical formulation. \S~III describes the three types of
hydrophobicity distribution that we use in the numerical simulations.
\S~IV outlines the quantitative measures used to describe the collective
hydrodynamics of JPs summarized and discussed in \S~V. \S~VI provides a
conclusion and discussion for future directions.
